XSFACE Analyses

### 2018-01-15 analysis-main/main_analyses_bll.Rmd
integrate hand detectors etc.
slight updates; ref new data file

```{r}
d <- read_csv("../data/consolidateddata/consolidated_data_3dets.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}
#d$face=d$faceVJ
#d$face=d$faceMT
d$face=d$faceOP
#d$face=d$handOP

>>>>

```{r}
d <- read_csv("../data/consolidateddata/consolidated_data_4dets.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}
#d$face=d$faceVJ
d$face=d$faceMT
#d$face=d$faceOP
#d$face=d$handOP
